```{r, echo=FALSE, message=FALSE}
library(RCurl)
library(dplyr)
library(stringr)
kathmandu = na.omit(read.csv("kathmandu.csv", na.strings = "")) #read csv assigning all the empty string as NA
kathmandu$district = "Kathmandu"
patan = na.omit(read.csv("patan.csv", na.strings = ""))
patan$district = "Lalitpur"
bhaktapur = na.omit(read.csv("bhaktapur.csv", na.strings = ""))
bhaktapur$district = "Bhaktapur"
palace = read.csv("palace.csv", na.strings = "")
valley = read.csv("valley.csv",na.strings = "")
pruscha = na.omit(rbind(kathmandu, bhaktapur, patan, valley, palace)) # merge all the dataframe by removing the empty rows
pruscha = rename(pruscha, id = S..No.)
pruscha$id = toupper(gsub("[^A-Za-z0-9.]","", pruscha$id))

onaCSVStream = getURI("http://ona.io/api/v1/data/49501.csv")
onadata = read.csv(textConnection(onaCSVStream), na.strings="n/a")
onaNA = filter(onadata, is.na(site_id))
onaNotNa = filter (onadata, !(is.na(site_id)))
onaNotNa$site_id = gsub(".*/","", onaNotNa$site_id)
onaNotNa$site_id = gsub("[^A-Za-z0-9.]","", onaNotNa$site_id)
onaNotNa$site_id = toupper(gsub("Garmin*","", onaNotNa$site_id))
onaKathmandu = filter (onaNotNa , district == "Kathmandu")
onaLalitpur = filter (onaNotNa, district == "Lalitpur")
onaBhaktapur = filter (onaNotNa, district == "Bhaktapur")
onaOtherDistrict = filter (onaNotNa, district == "other")

match = merge(onaNotNa, pruscha, by.x = "site_id", by.y = "id", all.x = F)
matchSummary = match %>% group_by(district.y) %>% summarise(Matched = n())
pruschaSummary = pruscha %>% group_by(district) %>% summarise(Total = n())
matchSummary = merge(matchSummary, pruschaSummary, by.x = "district.y", by.y = "district", all.y = T)
matchSummary$Matched[is.na(matchSummary$Matched)] = 0
matchSummary$Completion = ((matchSummary$Matched/matchSummary$Total)*100)
```




<!DOCTYPE html>
<html lang="en">
<head>

  <!-- Basic Page Needs
    –––––––––––––––––––––––––––––––––––––––––––––––––– -->
      <meta charset="utf-8">
        <title>Your page title here :)</title>
	  <meta name="description" content="">
	    <meta name="author" content="">
	    
  <!-- Mobile Specific Metas
    –––––––––––––––––––––––––––––––––––––––––––––––––– -->
      <meta name="viewport" content="width=device-width, initial-scale=1">
      
  <!-- FONT
    –––––––––––––––––––––––––––––––––––––––––––––––––– -->
      <link href="http://fonts.googleapis.com/css?family=Raleway:400,300,600" rel="stylesheet" type="text/css">
      
  <!-- CSS
    –––––––––––––––––––––––––––––––––––––––––––––––––– -->
      <link rel="stylesheet" href="css/normalize.css">
        <link rel="stylesheet" href="css/skeleton.css">
	<link rel="stylesheet" href="http://cdn.datatables.net/1.10.7/css/jquery.dataTables.min.css">	
  <!-- Favicon
    –––––––––––––––––––––––––––––––––––––––––––––––––– -->
     <!-- <link rel="icon" type="image/png" href="images/favicon.png">-->
      
</head>
<body ng-app="UNESCOApp">
<div class="container" ng-controller="mainCtrl">
<h2 class="title">UNESCO Submission Tracking</h2>
***
<div>
####Percentage Completed According to Pruscha Dataset
```{r, echo=FALSE, message=FALSE}
knitr::kable(matchSummary,col.names = c("District", "Accesed","Total Number in Pruscha","Percentage Complete"))
```

```{r, echo=FALSE, message=FALSE}
onaUnmatch = filter(onaNotNa, ! onaNotNa$site_id %in% match$site_id)
pruschaRemaning = filter (pruscha, ! pruscha$id %in% match$site_id)
```
<div class="row">
<div class="six columns">
**Note:** `r nrow(onaNA)` entries are submitted without any site ID.
</div>
<div class="six columns">
<span class="u-pull-right"><ul><li>generated on `r date()`</li></ul></span>
</div>
</div>
<center>
<div style="margin-top:70px">
<a ng-click="show(false)" class="button button-primary u-full-width" style="width:600px">List of Sites Yet to be Assesed</a>
</div>
</center>
</div>



<div ng-hide="tab">
##List of Sites Yet to be Assesed


<div class="row">

<div class="three columns">
<a class="button" href="#" ng-click="showKathmandu()">Kathmandu</a>
</div>

<div class="three columns">
<a class="button" href="#" ng-click="showLalitpur()">Lalitpur</a>
</div>

<div class="three columns">
<a class="button" href="#" ng-click="showBhaktapur()">Bhaktapur</a>
</div>

<div class="three columns">
<a class="button" href="#" ng-click="showOthers()">Others</a>
</div>

</div>






<div ng-show="kathmandu">
<h3>Kathmandu</h3>

```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Kathmandu"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```


</div>
<div ng-show="lalitpur">
<h3>Lalitpur</h3>
```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Lalitpur"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```

</div>
<div ng-show="bhaktapur">
<h3>Bhaktapur</h3>
```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Bhaktapur"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```
</div>
<div ng-show="others">
<h5>List of ID's in Ona Survey Not Found in Pruscha Inventory</h5>
```{r, echo=FALSE, message=FALSE}
knitr::kable(data.frame(onaUnmatch$site_id, onaUnmatch$tole_name, onaUnmatch$temple_name), 'html', table.attr='class="data_table"', col.names = c("ID", "Tole Name", "Temple Name"))
```


</div>



</div>

</div>
</body>
<script type="text/javascript" src="jquery.js"></script>
<script type="text/javascript" src="angular.min.js"></script>
<script type="text/javascript" src="js/jquery.dataTables.min.js"></script>
<script type="text/javascript" src="main.js"></script>
<script type="text/javascript">
	$(document).ready(function() {
		$('.data_table').DataTable({
			"bFilter": false,
			"bLengthChange": false,
			"iDisplayLength": 30
		});
	});

</script>
</html>
