---
title: "UNESCO Submission Tracking"
date: "generated on `r date()`"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(RCurl)
library(dplyr)
library(stringr)
kathmandu = na.omit(read.csv("kathmandu.csv", na.strings = "")) #read csv assigning all the empty string as NA
kathmandu$district = "Kathmandu"
patan = na.omit(read.csv("patan.csv", na.strings = ""))
patan$district = "Lalitpur"
bhaktapur = na.omit(read.csv("bhaktapur.csv", na.strings = ""))
bhaktapur$district = "Bhaktapur"
palace = read.csv("palace.csv", na.strings = "")
valley = read.csv("valley.csv",na.strings = "")
pruscha = na.omit(rbind(kathmandu, bhaktapur, patan, valley, palace)) # merge all the dataframe by removing the empty rows
pruscha = rename(pruscha, id = S..No.)
pruscha$id = toupper(gsub("[^A-Za-z0-9.]","", pruscha$id))

onaCSVStream = getURI("http://ona.io/api/v1/data/49501.csv")
onadata = read.csv(textConnection(onaCSVStream), na.strings="n/a")
onaNA = filter(onadata, is.na(site_id))
onaNotNa = filter (onadata, !(is.na(site_id)))
onaNotNa$site_id = gsub(".*/","", onaNotNa$site_id)
onaNotNa$site_id = gsub("[^A-Za-z0-9.]","", onaNotNa$site_id)
onaNotNa$site_id = toupper(gsub("Garmin*","", onaNotNa$site_id))
onaKathmandu = filter (onaNotNa , district == "Kathmandu")
onaLalitpur = filter (onaNotNa, district == "Lalitpur")
onaBhaktapur = filter (onaNotNa, district == "Bhaktapur")
onaOtherDistrict = filter (onaNotNa, district == "other")

match = merge(onaNotNa, pruscha, by.x = "site_id", by.y = "id", all.x = F)
matchSummary = match %>% group_by(district.y) %>% summarise(Matched = n())
pruschaSummary = pruscha %>% group_by(district) %>% summarise(Total = n())
matchSummary = merge(matchSummary, pruschaSummary, by.x = "district.y", by.y = "district", all.y = T)
matchSummary$Matched[is.na(matchSummary$Matched)] = 0
matchSummary$Completion = ((matchSummary$Matched/matchSummary$Total)*100)
```




<!DOCTYPE html>
<html lang="en">
<head>

<!-- Basic Page Needs
–––––––––––––––––––––––––––––––––––––––––––––––––– -->
<meta charset="utf-8">
<title>Your page title here :)</title>
<meta name="description" content="">
<meta name="author" content="">

<!-- Mobile Specific Metas
–––––––––––––––––––––––––––––––––––––––––––––––––– -->
<meta name="viewport" content="width=device-width, initial-scale=1">

<!-- FONT
–––––––––––––––––––––––––––––––––––––––––––––––––– -->
<!--<link href="http://fonts.googleapis.com/css?family=Raleway:400,300,600" rel="stylesheet" type="text/css">-->

<style>

/* latin */
@font-face {
  font-family: 'Raleway';
  font-style: normal;
  font-weight: 300;
  src: local('Raleway Light'), local('Raleway-Light'), url(http://fonts.gstatic.com/s/raleway/v9/-_Ctzj9b56b8RgXW8FArifk_vArhqVIZ0nv9q090hN8.woff2) format('woff2');
  unicode-range: U+0000-00FF, U+0131, U+0152-0153, U+02C6, U+02DA, U+02DC, U+2000-206F, U+2074, U+20AC, U+2212, U+2215, U+E0FF, U+EFFD, U+F000;
}
/* latin */
@font-face {
  font-family: 'Raleway';
  font-style: normal;
  font-weight: 400;
  src: local('Raleway'), url(http://fonts.gstatic.com/s/raleway/v9/0dTEPzkLWceF7z0koJaX1A.woff2) format('woff2');
  unicode-range: U+0000-00FF, U+0131, U+0152-0153, U+02C6, U+02DA, U+02DC, U+2000-206F, U+2074, U+20AC, U+2212, U+2215, U+E0FF, U+EFFD, U+F000;
}
/* latin */
@font-face {
  font-family: 'Raleway';
  font-style: normal;
  font-weight: 600;
  src: local('Raleway SemiBold'), local('Raleway-SemiBold'), url(http://fonts.gstatic.com/s/raleway/v9/xkvoNo9fC8O2RDydKj12b_k_vArhqVIZ0nv9q090hN8.woff2) format('woff2');
  unicode-range: U+0000-00FF, U+0131, U+0152-0153, U+02C6, U+02DA, U+02DC, U+2000-206F, U+2074, U+20AC, U+2212, U+2215, U+E0FF, U+EFFD, U+F000;
}

</style>


<!-- CSS
–––––––––––––––––––––––––––––––––––––––––––––––––– -->
<link rel="stylesheet" href="css/normalize.css">
<link rel="stylesheet" href="css/skeleton.css">
<link rel="stylesheet" href="css/jquery.dataTables.css">
<!-- Favicon
–––––––––––––––––––––––––––––––––––––––––––––––––– -->
<!-- <link rel="icon" type="image/png" href="images/favicon.png">-->

</head>
<body ng-app="UNESCOApp">
<div id="all_container" class="container" ng-controller="mainCtrl">
<!-- <h2 class="title">UNESCO Submission Tracking</h2> -->
<div>
####Percentage Completed According to Pruscha Dataset
```{r, echo=FALSE, message=FALSE}
knitr::kable(matchSummary,col.names = c("District", "Assessed","Total Number in Pruscha","Percentage Complete"))
```

```{r, echo=FALSE, message=FALSE}
onaUnmatch = filter(onaNotNa, ! onaNotNa$site_id %in% match$site_id)
pruschaRemaning = filter (pruscha, ! pruscha$id %in% match$site_id)
```
<div class="row">
<div class="six columns">
**Note:** `r nrow(onaNA)` entries are submitted without any site ID.
</div>

</div>

</div>



<div id="list_div" style="margin-top: 50px">
####List of Sites Yet to be Assessed


<div class="row">

<div class="four columns">
<a id="kathmandu_btn" class="button" href="#list_div" ng-click="showKathmandu()" onClick="changeClass">Kathmandu</a>
</div>

<div class="four columns">
<a id="lalitpur_btn" class="button" href="#list_div" ng-click="showLalitpur()">Lalitpur</a>
</div>

<div class="four columns">
<a id="bhaktapur_btn" class="button" href="#list_div" ng-click="showBhaktapur()">Bhaktapur</a>
</div>

</div>






<div ng-show="kathmandu">
<!-- <h3>Kathmandu</h3> -->

```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Kathmandu"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```


</div>
<div ng-show="lalitpur">
<!-- <h3>Lalitpur</h3> -->
```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Lalitpur"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```

</div>
<div ng-show="bhaktapur">
<!-- <h3>Bhaktapur</h3> -->
```{r, echo=FALSE, message=FALSE}
knitr::kable(filter (pruschaRemaning , district == "Bhaktapur"), 'html', table.attr='class="data_table"', col.names = c("ID", "Temple Name","Tole Name","District"))
```

</div>
<div style="margin-top:80px; margin-bottom: 20px">
<h4>List of IDs in Ona Survey Not Found in Pruscha Inventory</h4>
```{r, echo=FALSE, message=FALSE}
knitr::kable(data.frame(onaUnmatch$site_id, onaUnmatch$tole_name, onaUnmatch$temple_name), 'html', table.attr='class="data_table"', col.names = c("ID", "Tole Name", "Temple Name"))
```


</div>



</div>

</div>
</body>
<script type="text/javascript" src="jquery.js"></script>
<script type="text/javascript" src="angular.min.js"></script>
<script type="text/javascript" src="js/jquery.dataTables.min.js"></script>
<script type="text/javascript" src="main.js"></script>
<script type="text/javascript">
$(document).ready(function() {
$('.data_table').DataTable({
"bFilter": true,
"bLengthChange": false,
"iDisplayLength": 30,
});
$("div.toolbar").html('Kathmandu');
});


</script>
</html>
